\documentclass{armymemo}

\address{United States Military Academy}
\address{Electrical Engineering and Computer Science}
\address{West Point, NY 10996}

\author{Maria R. Ebling}
\rank{Assistant Professor}
\title{Project Advisor}

\cadet{Harry Q. Bovik}
\cadettitle{Principle Investigator}
\company{F-1}
\newcommand{\CourseNum}{CS388}
\newcommand{\Credits}{2.0} %% Choices: 1.0, 2.0, 3.0
\newcommand{\Hours}{80}    %% Choices: 40,  80,  120
\newcommand{\Term}{23-1}

\officesymbol{MADN-EECS-CS}
\signaturedate{\today}
\addmemoline{MEMORANDUM THRU Computer Science Program Director, Department of Electrical Engineering and Computer Science, LTC W. Robert Harrison}
\addmemoline{FOR Head, Department of Electrical Engineering and Computer Science, COL James J. Raftery}
\subject{Request Approval of Independent Study Course \CourseNum\ for Term \Term}

\begin{document}

\begin{enumerate}
\item Project Title: Research Project Title
\item Project Background \& Summary: This \CourseNum\ course will involve doing something interesting. In this course, CDT Bovik will investigate...
\item Project Advisor \& Meeting Location: The faculty advisor for this project will be Dr. Ebling. She will meet with Cadet Bovik at least once a week in TH1123 to review progress and provide guidance.
\item Project Goals: This project will be completed during the AY \Term\ term with the following goals:
\begin{enumerate}
    \item Understand...
    \item Investigate...
    \item Experiment...
    \item Analyze...
\end{enumerate}
\item Project Deliverables:
\begin{center}
\begin{tabular}{|l|l|}
\hline
     Lesson 1 & Initial meeting \\ \hline
     Lesson 10 & Milestone 1 \\ \hline
     Lesson 20 & Milestone 2 \\ \hline
     Lesson 30 & Milestone 3 \\ \hline
     Lesson 40 & Final paper due \\ \hline
\end{tabular}
\end{center}
\item Grades: The course is worth 1000 points. Students will be evaluated at the 6-week, 10-week, 15-week, and Final reporting periods; the undersigned’s performance will be assessed by the project adviser in each quarter of the course out of 250 course points.  If any deliverables projected to be completed are not, the adviser will assess accordingly.
\item Project Presentation Format: Cadet Bovik will write a short paper summarizing his research suitable for publication in a conference such as... The paper should be 4-6 double-column, single-spaced pages in length in ACM conference format.
\item Academic Background: Cadet Bovik is a Computer Science major in the class of 2024; his CQPA is 1.234 and last term's TQPA was 5.678 for 20.0 credit hours. If approved, this course would be his 6th academic course this semester.
\item Requested Academic Credit: \Credits\ credits for the \Hours\ hours attributed to the \CourseNum\ course.
\end{enumerate}

\end{document}
